ShinyMICE: Investigate relations in incomplete datasets to inform imputation model

### 2020-03-12 4.ShinyMICE/inspect_incomplete_data.Rmd

---
title: "Investigate relations in incomplete datasets to inform imputation model"
output:
  html_document:
    df_print: paged
---

@@

```{r}
# plot this for each missingness indicator
vars <- names(dat)
vars %>%
  map(~{ggplot(data=dat, aes(x = age, fill = is.na(.data[[.x]]))) +
  geom_histogram(aes(y = 100 * ..density..),
                 alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Percentage observed") +
  scale_fill_manual(
    name = .x,
    breaks = c("FALSE", "TRUE"),
    labels = c("observed", "missing"),
    values = c("#006CC2", "#B61A51")
  )})

>>>>

---
title: "ShinyMICE: Investigate relations in incomplete datasets to inform imputation model"
output:
  html_document:
    df_print: paged
---

@@

```{r}
# plot this for each missingness indicator
vars <- names(dat)
vars %>%
  map(~{ggplot(data=dat, aes(x = age, fill = is.na(.data[[.x]]))) +
  geom_histogram(alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Count of cases") +
  scale_fill_manual(
    name = .x,
    breaks = c("FALSE", "TRUE"),
    labels = c("observed", "missing"),
    values = c("#006CC2", "#B61A51")
  )})
